\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{blindtext}
\usepackage[letterpaper,margin=0.8in]{geometry}
\usepackage{fancyhdr}
\usepackage{helvet}

\pagestyle{empty}
\pagestyle{fancy}
\fancyhf{}
\lhead{Name:}
\rhead{\textit{December 23, 2020}}
\cfoot{Page \thepage}

\begin{document}

\section*{Factor}
{Remove the largest common factor from each term in the expressions below.}

\begin{large}
\begin{enumerate}
\item \quad $6x + 3y$

\addvspace{0.5in}

\item \quad $10x + 12y$

\addvspace{0.5in}

\item \quad $28x + 21$

\addvspace{0.5in}

\item \quad $6f - 6$

\addvspace{0.5in}

\item \quad $18ax - 15ay$

\addvspace{0.5in}

\item \quad $-5mx - 10my$

\addvspace{0.5in}

\item \quad $15ab - 3b$

\addvspace{0.5in}

\item \quad $12s + 48bs$

\addvspace{0.5in}

\end{enumerate}
\end{large}

\pagebreak

\section*{Solving Equations}
\begin{large}
{When you solve equations for the value of an unknown variable, quite often the hardest question is deciding which operation to undo first.
Below, which operation should you undo first?}

\begin{enumerate}
\item \quad $2x + 7 = 9$

What do you do first?

	\begin{enumerate}
     	\item{Subtract 2 from each side}
      	\item{Subtract 7 from each side}
      	\item{Divide both side by two}
      	\item{Subtract 9 from both sides}
    \end{enumerate}

\addvspace{0.4in}

\item \quad $3(5x + 1) = 27$

What do you do first?

	\begin{enumerate}
      	\item{Subtract 1 from both sides}
      	\item{Divide both sides by 3}
      	\item{Divide both sides by 5}
     	\item{Simplify the left-hand side using the distributive property}
    \end{enumerate}

\addvspace{0.4in}

\item \quad $3x + 5 = -x - 11$

What do you do first?

	\begin{enumerate}
      	\item{Add x to both sides}
      	\item{Subtract 5 from both sides}
      	\item{Subtract 11 from both sides}
      	\item{Add 3x to both sides}
     	\item{Divide both sides by 3}
    \end{enumerate}

\addvspace{0.4in}

\end{enumerate}
\end{large}


\pagebreak

\section*{Solving Equations}
\begin{large}
{Solve each equation for the value of the unknown variable. Pay careful attention to which operation to do first.}

\begin{enumerate}
\item \quad $5x = x - 8$

\begin{tabular}{p{0.3\textwidth}|p{0.3\textwidth}|p{0.2\textwidth}}
LHS & RHS & What to do \\
\hline
$5x$ & $x - 8$ & \\
& & \\
& & \\
& & \\
& & \\
& & \\
& & \\
\end{tabular}

\addvspace{0.3in}

\item \quad $2x - 10 = 6x$

\begin{tabular}{p{0.3\textwidth}|p{0.3\textwidth}|p{0.2\textwidth}}
LHS & RHS & What to do \\
\hline
$2x - 10$ & $6x$ & \\
& & \\
& & \\
& & \\
& & \\
& & \\
& & \\
\end{tabular}

\addvspace{0.3in}

\item \quad $12 + \dfrac{2}{5}x = 16$

\begin{tabular}{p{0.3\textwidth}|p{0.3\textwidth}|p{0.2\textwidth}}
LHS & RHS & What to do \\
\hline
$12 + \dfrac{2}{5}x$ & $16$ & \\
& & \\
& & \\
& & \\
& & \\
& & \\
& & \\
\end{tabular}

\addvspace{0.3in}
\end{enumerate}

\end{large}


\end{document}